Inefficient Concessions and Mediation

### 2023-08-07 draft_narrow.tex
add comparative statics on p

When the low type's patience level $\de_l$ increases, the high type's patience threshold decreases because a smaller gift is required to disincentivize the low type from pretending to be a high type. Finally, and perhaps surprisingly, the patience threshold is increasing in $p$. This happens because the gift must be larger in order to discourage low types from giving a gift, and this effect outweighs the increased attractiveness to the high type that comes directly from the increased probability of positive impacts from the future material value.\footnote{Comparative statics calculations available from the authors upon request.}

>>>>

When the low type's patience level $\de_l$ increases, the high type's patience threshold decreases because a smaller gift is required to disincentivize the low type from pretending to be a high type. Finally, the patience threshold is decreasing in $p$, the proportion of cooperative types in the population. This happens because a higher $p$ increases the chances of cooperation, a reciprocated gift, and the benefits from the associated public goods. This gain outweighs the cost of giving a larger gift, which is necessary to deter the low type from mimicking the high type when the probability of receiving a gift increases with $p$. In contrast, in the model with no material value---where the incentives are the same as in the model of the next section where material value can be destroyed---the need to give a larger gift is exactly offset by the increased value of cooperation when there is no material value. Thus, an increase in $p$ increases the range of patience levels under which cooperation can be achieved when there is material value but makes no change if there is no material value.\footnote{Comparative statics calculations available from the authors upon request.}
